---
title: "Workflow - Utsjoki smolts"
author: "hennip"
date: "25 August 2017"
output: html_document
---

```{r echo=FALSE, cache= F}
knitr::read_chunk('01-Data/draw-some-data.R')
```

## Intro

These are the notes and workflow documentation of Utsjoki smolt count model. All material (except data) is stored in Github <https://github.com/hennip/Utsjoki-smolts>

### Functions, packages and paths

First run from 00-Functions

* packages-and-paths.r
* tidy-functions.r
* my-palette.r

```{r include=FALSE}
source("00-Functions/packages-and-paths.r")
source("00-Functions/tidy-functions.r")
source("00-Functions/my-palette.r")

```


### Data

* Annual video count data from 61 days in June-July

Run script

* 01-Data/tidy-smolts-data.r

```{r include=FALSE}
source("01-Data/tidy-smolts-data.r")

```

```{r draw-some-data-temp}
```

```{r draw-some-data-flow}
```

```{r draw-some-data-smolts}
```


## Priors
```{r include=FALSE}
#source("prior-obsprop-vs-flow.r")
#source("prior-travel-time-vs-flow.r")
#source("prior-obsprop-vs-flow.r")

```


## Model

## MCMC diagnostics

## Posterior distributions



